IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-02-27 codes/R/cohorts_nc.Rnw
minor changes to text tables

# fill in differences
regs.ext <- list()
regs.int <- list()
for (r in 1:nrow(regcoeffs)) {
  regs.ext[[r]] <- lm(EXT ~ as.factor(incq) + age, data=subset(items.scored[[8]], cohort==regcoeffs[r,1] & sex==regcoeffs[r,2]))
  regcoeffs[r,3] <- round(regs.ext[[r]]$coefficients["as.factor(incq)5"],2)
  regs.int[[r]] <- lm(INT ~ as.factor(incq) + age, data=subset(items.scored[[8]], cohort==regcoeffs[r,1] & sex==regcoeffs[r,2]))
  regcoeffs[r,4] <- round(regs.int[[r]]$coefficients["as.factor(incq)5"],2)
}

>>>>

# fill in differences
regs.ext <- list()
regs.int <- list()
for (r in 1:nrow(regcoeffs)) {
  regs.ext[[r]] <- lm(EXT ~ as.factor(incq) + age, data=subset(scores2plot, cohort==regcoeffs[r,1] & sex==regcoeffs[r,2]))
  regcoeffs[r,3] <- round(regs.ext[[r]]$coefficients["as.factor(incq)5"],2)
  regs.int[[r]] <- lm(INT ~ as.factor(incq) + age, data=subset(scores2plot, cohort==regcoeffs[r,1] & sex==regcoeffs[r,2]))
  regcoeffs[r,4] <- round(regs.int[[r]]$coefficients["as.factor(incq)5"],2)
}
